Applications of limited information strategies in Menger's game

### 2015-08-25 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
deflated $..$ to \(..\)

\keywords{Menger's property, Menger's game, limited information strategies}
% \begin{keyword}
%   Proximal\sep absolutely proximal\sep Corson compact\sep uniform space\sep $W$-space
% \end{keyword}

@@

\begin{definition}
  A space $X$ is Menger if for every sequence $\<\mc U_0,\mc U_1,\dots\>$
  of open covers of $X$ there exists a sequence
  $\<\mc F_0,\mc F_1,\dots\>$ such that $\mc F_n\subseteq \mc U_n$,
  $|\mc F_n|<\omega$, and $\bigcup_{n<\omega}\mc F_n$ is a cover of $X$.
\end{definition}

@@

\begin{proposition}
  $X$ is $\sigma$-compact
    $\Rightarrow$
  $X$ is Menger
    $\Rightarrow$
  $X$ is Lindel\"of.
\end{proposition}

None of these implications may be reversed; the irrationals are a simple example
of a Lindel\"of space which is not Menger, and we'll see several examples of
Menger spaces which are not $\sigma$-compact.

@@

\begin{definition}
  For each cover $\mc U$ of $X$, $S\subseteq X$ is \term{$\mc U$-finite} if
  there exists a finite subcollection of $\mc U$ which covers $C$.
\end{definition}

Of course, a compact space is $\mc U$-finite for all open covers $\mc U$.

\begin{game}
  Let $\menGame{X}$ denote the \term{Menger game} with players $\pl C$, $\pl F$.
  In round $n$, $\pl C$ chooses an open cover $\mc U_n$, followed by $\pl F$
  choosing a $\mc U_n$-finite subset $F_n$ of $X$.

  $\pl F$ wins the game if $X = \bigcup_{n<\omega}F_n$,
  and $\pl C$ wins otherwise.
\end{game}

\begin{theorem}
  A space $X$ is Menger if and only if $\pl C\notwin\menGame{X}$
  \cite{MR1544773}.
\end{theorem}

The typical characterization of the Menger game involves $\pl F$ choosing
a finite subcollection $\mc F_n$ of $\mc U_n$, but it is easy to see that the
characterization given above is equivalent, and will be convenient for use
in our proofs.

@@

\begin{proposition}
  $X$ is compact if and only if
  $\pl F \tactwin \menGame{X}$ if and only if
  $\pl F \ktactwin{k} \menGame{X}$.
\end{proposition}

\begin{proof}
  If $\sigma$ is a winning $k$-tactic, then for each open cover $\mc U$,
  $\sigma$ defeats the attack $\<\mc U,\mc U,\dots\>$. Then
  \[
    \bigcup_{i\leq k} \sigma(\<\underbrace{\mc U,\dots,\mc U}_i\>) = X
  \]
  and $X$ is $\mc U$-finite.
\end{proof}

Essentially, because $\pl C$ may repeat the same finite sequence of open covers,
$\pl F$ needs to be seeded with knowledge of the round number to prevent being
trapped in a loop.

If $\pl F$'s memory of $\pl C$'s past moves is bounded, then
there is no need to consider more than the two most recent moves. The
intuitive reason is that $\pl C$ could simply play the same cover repeatedly
until $\pl F$'s memory is exhausted, in which case $\pl F$ would only ever
see the change from one cover to another.

\begin{theorem}
  For each $k<\omega$, $F \kmarkwin{(k+2)} \menGame{X}$
  if and only if $F \kmarkwin2 \menGame{X}$.
\end{theorem}

\begin{proof}
  Let $\sigma$ be a winning $(k+2)$-mark. We define the $2$-mark $\tau$ as
  follows:
    \[
      \tau(\<\mc U\>,0)
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U,\dots,\mc U}_{m+1}\>,m)
    \]
    \[
      \tau(\<\mc U,\mc V\>,n+1)
        =
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U,\dots,\mc U}_{k+1-m},
          \underbrace{\mc V,\dots,\mc V}_{m+1}
        \>,(n+1)(k+2)+m)
    \]

  Let $\<\mc U_0,\mc U_1,\dots\>$ be an attack by $\pl C$ against $\tau$.
  Then consider the attack
    \[
      \<
        \underbrace{\mc U_0,\dots,\mc U_0}_{k+2},
        \underbrace{\mc U_1,\dots,\mc U_1}_{k+2},
        \dots
      \>
    \]
  by $\pl C$ against $\sigma$. Since $\sigma$ is a winning $(k+2)$-mark,
    \[
      X
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U_0,\dots,\mc U_0}_{m+1}\>,m)
      \cup
      \bigcup_{n<\omega}
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U_n,\dots,\mc U_n}_{k+1-m},
          \underbrace{\mc U_{n+1},\dots,\mc U_{n+1}}_{m+1}
        \>,(n+1)(k+2)+m)
    \]
    \[
      =
      \tau(\<\mc U_0\>,0)
      \cup
      \bigcup_{n<\omega}
      \tau(\<\mc U_n,\mc U_{n+1}\>,n+1)
    \]
  Thus $\tau$ is a winning $2$-mark.
\end{proof}

A natural question arises: is there an example of a space $X$ for which
$\pl F\kmarkwin{2}\menGame{X}$ but $\pl F\notmarkwin\menGame{X}$? We quickly
see that perhaps the simplest example of a Lindel\"of non-$\sigma$-compact
space has this property.

\begin{definition}
  For any cardinal $\kappa$, let $\oneptlind\kappa=\kappa\cup\{\infty\}$ denote
  the \term{one-point Lindel\"of-ication} of discrete $\kappa$, where points in
  $\kappa$ are isolated, and the neighborhoods of $\infty$ are the co-countable
  sets containing it.
\end{definition}

\begin{theorem}
  $\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}$.
\end{theorem}

\begin{proof}
  This result will later follow from the fact that
  $\oneptlind\omega_1$ is not a $\sigma$-compact space (all its compact subsets
  are finite).

  For now, let $\sigma$ be a Markov strategy for $\pl F$. For
  each $\alpha<\omega_1$, let $\mc U_\alpha$ be the open cover
  $\{\{\beta\}:\beta<\alpha\}\cup\{\oneptlind{\omega_1}\setminus\alpha\}$ of
  $\oneptlind{\omega_1}$, and set $F(\alpha,n)$ to be the finite set
  $\alpha\cap\sigma(\<\mc U_\alpha\>,n)$.

  If
    $
      P_n =
      \{\beta: \beta < \alpha < \omega_1 \Rightarrow \beta \in F(\alpha,n)\}
    $,
  then $P_n\subseteq F(\sup(P_n)+1,n)$. Thus $P_n$ is finite for $n<\omega$.
  Choose $\beta\in\omega_1\setminus \bigcup_{n<\omega}P_n$
  and $\alpha_n>\beta$ such that $\beta\not\in F(\alpha_n,n)$.
  Then $\pl C$ may attack
  $\sigma$ with $\<\mc U_{\alpha_0}, \mc U_{\alpha_1},\dots\>$,
  and it follows that
  $\beta\not\in \bigcup_{n<\omega}F(\alpha_n,n)$ and
  $\beta\not\in \bigcup_{n<\omega}\sigma(\<\mc U_{\alpha_n}\>,n)$.
\end{proof}

The greatest advantage of a strategy which has knowledge of two or more previous
moves of the opponent, versus only knowledge of the most recent move, is the
ability to react to changes from one round to the next. It's this ability to
react that will give $\pl F$ her winning $2$-Markov strategy in the Menger
game on $\oneptlind\omega_1$.

For inspiration, we turn to a game whose $n$-tactics were studied by Marion
Scheepers in \cite{MR1129143} which has similar goals to the Menger game when
played upon $\oneptlind\kappa$.

\begin{game}
  Let $\cloFillStrictGame\kappa$ denote the \term{strict union filling game}
  with two players $\pl C$, $\pl F$. In round $0$, $\pl C$ chooses
  $C_0\in[\kappa]^{\leq\omega}$, followed by $\pl F$ choosing
  $F_0\in[\kappa]^{<\omega}$. In round $n+1$, $\pl C$ chooses
  $C_{n+1}\in[\kappa]^{\leq\omega}$ such that $C_{n+1}\supset C_n$, followed
  by $\pl F$ choosing $F_{n+1}\in[\kappa]^{<\omega}$.

  $\pl F$ wins the game if
  $\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n$; otherwise, $\pl C$
  wins.
\end{game}

In $\menGame{\oneptlind\kappa}$, $\pl C$ essentially chooses a countable set
to not include in her neighborhood of $\infty$, followed by $\pl F$ choosing
a finite subset of this complement to cover during each round. Thus,
$\pl F$ need only be concerned with the \textit{intersection} of the
countable sets chosen by $\pl C$ in $\menGame{\oneptlind\kappa}$, rather
than the union as in $\cloFillStrictGame\kappa$.

Another difference: Scheepers required that $\pl C$ always choose strictly
growing countable sets. The reasoning is clear: if the goal is to study tactics,
then $\pl C$ cannot be allowed to trap $\pl F$ in a loop by repeating the same
moves. But by eliminating this requirement, the study can then turn to Markov
strategies, bringing the game further in line with the Menger game played upon
$\oneptlind\kappa$.

We introduce a few games to make the relationship between Scheeper's
$\cloFillStrictGame\kappa$ and $\menGame{\oneptlind\kappa}$ more precise.

\begin{game}
  Let $\cloFillGame\kappa$ denote the
  \term{union filling game} which proceeds analogously
  to $\cloFillStrictGame\kappa$, except that $\pl C$'s restriction in round $n+1$
  is reduced to $C_{n+1}\supseteq C_n$.
\end{game}

\begin{game}
  Let $\cloFillInitialGame\kappa$ denote the
  \term{initial filling game} which proceeds analogously
  to $\cloFillGame\kappa$, except that $\pl F$ wins whenever
  $\bigcup_{n<\omega}F_n\supseteq C_0$.
\end{game}

\begin{game}
  Let $\cloFillIntGame\kappa$ denote the
  \term{intersection filling game} which proceeds analogously
  to $\cloFillInitialGame\kappa$, except that $\pl C$ may choose any
  $C_n\in[\kappa]^{\leq\omega}$ each round, and $\pl F$ wins whenever
  $\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n$.
\end{game}

@@

\begin{theorem}
For any cardinal $\kappa>\omega$ and integer $k<\omega$,
Figure \ref{fillingGamesDiagram} holds.
\end{theorem}

\begin{proof}
  $\pl F \kmarkwin{k}\menGame{\oneptlind\kappa}
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillIntGame\kappa$:
  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\menGame{\oneptlind\kappa}$. Let $\mc U(C)$ (resp. $\mc U(s)$) convert each
  countable subset $C$ of $\kappa$ (resp. finite sequence $s$ of such subsets)
  into the open cover $[C]^1\cup\{\oneptlind\kappa\setminus C\}$
  (resp. finite sequence of such open covers). Then $\tau$ defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      C\cap\sigma(\mc U(s\concat\<C\>),n)
    \]
  is a winning $k$-mark for $\pl F$ in $\cloFillIntGame\kappa$.

  $\pl F \kmarkwin{k}\cloFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\menGame{\oneptlind\kappa}$:
  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\cloFillIntGame\kappa$. Let $C(\mc U)$ (resp. $C(s)$) convert each open
  cover $\mc U$ of $\oneptlind\kappa$ (resp. finite sequence $s$ of such covers)
  into a countable set $C$ which is the complement of some neighborhood of
  $\infty$ in $\mc U$ (resp. finite sequence of such countable sets).
  Then $\tau$ defined by
    \[
      \tau(s\concat\<\mc U\>,n)
        =
      (\oneptlind\kappa\setminus C(\mc U))
        \cup
      \sigma(C(s\concat\<\mc U)\>),n)
    \]
  is a winning $k$-mark for $\pl F$ in $\menGame{\oneptlind\kappa}$.

  $\pl F \kmarkwin{k}\cloFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillInitialGame\kappa$:
  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\cloFillIntGame\kappa$. $\sigma$ is also a winning $k$-mark for $\pl F$
  in $\cloFillInitialGame\kappa$.

  $\pl F \kmarkwin{k}\cloFillInitialGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillGame\kappa$: Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\cloFillInitialGame\kappa$. For each finite sequence $s$, let $t\preceq s$ mean $t$
  is a final subsequence of $s$. Then $\tau$ defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      \bigcup_{t\preceq s, m\leq n}
      \sigma(t\concat\<C\>,m)
    \]
  is a winning $k$-mark for $\pl F$ in $\cloFillGame\kappa$.

  $\pl F \kmarkwin{k}\cloFillGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillInitialGame\kappa$:
  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\cloFillGame\kappa$. $\sigma$ is also a winning $k$-mark for $\pl F$
  in $\cloFillInitialGame\kappa$.

  $\pl F \ktactwin{k}\cloFillStrictGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillGame\kappa$:
  Let $\sigma$ be a winning $k$-tactic for $\pl F$ in
  $\cloFillStrictGame\kappa$. For each countable subset $C$ of $\kappa$, let $C+n$
  be the union of $C$ with the $n$ least ordinals in $\kappa\setminus C$.
  Then $\tau$ defined by
    \[
      \tau(\<C_0,\dots,C_i\>,n)
        =
      \sigma(\<C_0+(n-i),\dots,C_i+n\>)
    \]
  is a winning $k$-mark for $\pl F$ in $\cloFillGame\kappa$.
\end{proof}

While we have not proven a direct implication between the Menger game and
Scheeper's original filling game, Scheepers introduced the statement
$\alcompS\kappa$ relating to the almost-compatability of functions
from countable subsets of $\kappa$ into $\omega$ which may be applied to
both.

\begin{definition}
  For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with
  $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$.
  If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible}
  ($f\alcomp g$).
\end{definition}

\begin{definition}
  $\alcompS\kappa$ states that there exist functions
  $f_A:A\to\omega$ for each $A\in[\kappa]^{\leq\omega}$ such that
  $|\{\alpha\in A:f_A(\alpha)\leq n\}|<\omega$ for all $n<\omega$ and
  $f_A\alcomp f_B$ for all $A,B\in[\kappa]^\omega$.
  \footnote{
  This is equivalent to the original characterization given in
  \cite{MR1129143}: there exist injections $g_A:A\to\omega$
  such that $g_A\alcomp g_B$ for all $A,B\in[\kappa]^\omega$ and $A\subset B$.
  }
\end{definition}

Scheepers went on to show that $\alcompS\kappa$ implies
$\pl F \ktactwin2 \cloFillStrictGame\kappa$. This proof, along with the following
facts, give us inspiration for
finding a winning $2$-Markov strategy in the Menger game played on
$\oneptlind\kappa$.

\begin{theorem}
  $\alcompS{\omega_1}$ and $\kappa>2^\omega\Rightarrow\neg\alcompS\kappa$
  are theorems of $ZFC$.
  $\alcompS{2^\omega}$ is a theorem of $ZFC+CH$ and consistent with
  $ZFC+\neg CH$.
\end{theorem}

\begin{proof}
  For $\alcompS{\omega_1}$, look at pg. 70 of \cite{MR597342}; this of course
  implies $\alcompS{2^\omega}$ under $CH$.
  $\neg\alcompS{(2^\omega)^+}$ is shown by a cardinality argument
  in \cite{MR1129143}.
  The consistency result under $ZFC+\neg CH$
  is a lemma for the main theorem in \cite{MR1129143}.
\end{proof}

@@

%     &
%     &
%     \pl F \ktactwin2\cloFillStrictGame\kappa \\
%   };
%   \path[>=latex,->]
%     (m-2-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2)
%     (m-2-1) edge (m-3-3)
%     (m-1-2) edge (m-2-2)
%     (m-1-3) edge (m-2-3)
%     (m-3-3) edge (m-2-3);
%   \path[>=latex,<->]
%     (m-1-2) edge (m-1-3)
%     (m-2-2) edge (m-2-3);
% \end{tikzpicture}
\end{center}
\caption{Diagram of Filling/Menger game implications with $\alcompS\kappa$}
\label{fillingGamesDiagram2}
\end{figure}

>>>>

\keywords{Menger's property, Menger's game, limited information strategies}
% \begin{keyword}
%   Proximal\sep absolutely proximal\sep Corson compact\sep uniform space\sep \(W\)-space
% \end{keyword}

@@

\begin{definition}
  A space \(X\) is Menger if for every sequence \(\<\mc U_0,\mc U_1,\dots\>\)
  of open covers of \(X\) there exists a sequence
  \(\<\mc F_0,\mc F_1,\dots\>\) such that \(\mc F_n\subseteq \mc U_n\),
  \(|\mc F_n|<\omega\), and \(\bigcup_{n<\omega}\mc F_n\) is a cover of \(X\).
\end{definition}

@@

\begin{proposition}
  \(X\) is \(\sigma\)-compact
    \(\Rightarrow\)
  \(X\) is Menger
    \(\Rightarrow\)
  \(X\) is Lindel\"of.
\end{proposition}

None of these implications may be reversed; the irrationals are a simple example
of a Lindel\"of space which is not Menger, and we'll see several examples of
Menger spaces which are not \(\sigma\)-compact.

@@

\begin{definition}
  For each cover \(\mc U\) of \(X\), \(S\subseteq X\) is \term{\(\mc U\)-finite} if
  there exists a finite subcollection of \(\mc U\) which covers \(C\).
\end{definition}

Of course, a compact space is \(\mc U\)-finite for all open covers \(\mc U\).

\begin{game}
  Let \(\menGame{X}\) denote the \term{Menger game} with players \(\pl C\), \(\pl F\).
  In round \(n\), \(\pl C\) chooses an open cover \(\mc U_n\), followed by \(\pl F\)
  choosing a \(\mc U_n\)-finite subset \(F_n\) of \(X\).

  \(\pl F\) wins the game if \(X = \bigcup_{n<\omega}F_n\),
  and \(\pl C\) wins otherwise.
\end{game}

\begin{theorem}
  A space \(X\) is Menger if and only if \(\pl C\notwin\menGame{X}\)
  \cite{MR1544773}.
\end{theorem}

The typical characterization of the Menger game involves \(\pl F\) choosing
a finite subcollection \(\mc F_n\) of \(\mc U_n\), but it is easy to see that the
characterization given above is equivalent, and will be convenient for use
in our proofs.

@@

\begin{proposition}
  \(X\) is compact if and only if
  \(\pl F \tactwin \menGame{X}\) if and only if
  \(\pl F \ktactwin{k} \menGame{X}\).
\end{proposition}

\begin{proof}
  If \(\sigma\) is a winning \(k\)-tactic, then for each open cover \(\mc U\),
  \(\sigma\) defeats the attack \(\<\mc U,\mc U,\dots\>\). Then
  \[
    \bigcup_{i\leq k} \sigma(\<\underbrace{\mc U,\dots,\mc U}_i\>) = X
  \]
  and \(X\) is \(\mc U\)-finite.
\end{proof}

Essentially, because \(\pl C\) may repeat the same finite sequence of open covers,
\(\pl F\) needs to be seeded with knowledge of the round number to prevent being
trapped in a loop.

If \(\pl F\)'s memory of \(\pl C\)'s past moves is bounded, then
there is no need to consider more than the two most recent moves. The
intuitive reason is that \(\pl C\) could simply play the same cover repeatedly
until \(\pl F\)'s memory is exhausted, in which case \(\pl F\) would only ever
see the change from one cover to another.

\begin{theorem}
  For each \(k<\omega\), \(F \kmarkwin{(k+2)} \menGame{X}\)
  if and only if \(F \kmarkwin2 \menGame{X}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) be a winning \((k+2)\)-mark. We define the \(2\)-mark \(\tau\) as
  follows:
    \[
      \tau(\<\mc U\>,0)
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U,\dots,\mc U}_{m+1}\>,m)
    \]
    \[
      \tau(\<\mc U,\mc V\>,n+1)
        =
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U,\dots,\mc U}_{k+1-m},
          \underbrace{\mc V,\dots,\mc V}_{m+1}
        \>,(n+1)(k+2)+m)
    \]

  Let \(\<\mc U_0,\mc U_1,\dots\>\) be an attack by \(\pl C\) against \(\tau\).
  Then consider the attack
    \[
      \<
        \underbrace{\mc U_0,\dots,\mc U_0}_{k+2},
        \underbrace{\mc U_1,\dots,\mc U_1}_{k+2},
        \dots
      \>
    \]
  by \(\pl C\) against \(\sigma\). Since \(\sigma\) is a winning \((k+2)\)-mark,
    \[
      X
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U_0,\dots,\mc U_0}_{m+1}\>,m)
      \cup
      \bigcup_{n<\omega}
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U_n,\dots,\mc U_n}_{k+1-m},
          \underbrace{\mc U_{n+1},\dots,\mc U_{n+1}}_{m+1}
        \>,(n+1)(k+2)+m)
    \]
    \[
      =
      \tau(\<\mc U_0\>,0)
      \cup
      \bigcup_{n<\omega}
      \tau(\<\mc U_n,\mc U_{n+1}\>,n+1)
    \]
  Thus \(\tau\) is a winning \(2\)-mark.
\end{proof}

A natural question arises: is there an example of a space \(X\) for which
\(\pl F\kmarkwin{2}\menGame{X}\) but \(\pl F\notmarkwin\menGame{X}\)? We quickly
see that perhaps the simplest example of a Lindel\"of non-\(\sigma\)-compact
space has this property.

\begin{definition}
  For any cardinal \(\kappa\), let \(\oneptlind\kappa=\kappa\cup\{\infty\}\) denote
  the \term{one-point Lindel\"of-ication} of discrete \(\kappa\), where points in
  \(\kappa\) are isolated, and the neighborhoods of \(\infty\) are the co-countable
  sets containing it.
\end{definition}

\begin{theorem}
  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\).
\end{theorem}

\begin{proof}
  This result will later follow from the fact that
  \(\oneptlind\omega_1\) is not a \(\sigma\)-compact space (all its compact subsets
  are finite).

  For now, let \(\sigma\) be a Markov strategy for \(\pl F\). For
  each \(\alpha<\omega_1\), let \(\mc U_\alpha\) be the open cover
  \(\{\{\beta\}:\beta<\alpha\}\cup\{\oneptlind{\omega_1}\setminus\alpha\}\) of
  \(\oneptlind{\omega_1}\), and set \(F(\alpha,n)\) to be the finite set
  \(\alpha\cap\sigma(\<\mc U_\alpha\>,n)\).

  If
    \(
      P_n =
      \{\beta: \beta < \alpha < \omega_1 \Rightarrow \beta \in F(\alpha,n)\}
    \),
  then \(P_n\subseteq F(\sup(P_n)+1,n)\). Thus \(P_n\) is finite for \(n<\omega\).
  Choose \(\beta\in\omega_1\setminus \bigcup_{n<\omega}P_n\)
  and \(\alpha_n>\beta\) such that \(\beta\not\in F(\alpha_n,n)\).
  Then \(\pl C\) may attack
  \(\sigma\) with \(\<\mc U_{\alpha_0}, \mc U_{\alpha_1},\dots\>\),
  and it follows that
  \(\beta\not\in \bigcup_{n<\omega}F(\alpha_n,n)\) and
  \(\beta\not\in \bigcup_{n<\omega}\sigma(\<\mc U_{\alpha_n}\>,n)\).
\end{proof}

The greatest advantage of a strategy which has knowledge of two or more previous
moves of the opponent, versus only knowledge of the most recent move, is the
ability to react to changes from one round to the next. It's this ability to
react that will give \(\pl F\) her winning \(2\)-Markov strategy in the Menger
game on \(\oneptlind\omega_1\).

For inspiration, we turn to a game whose \(n\)-tactics were studied by Marion
Scheepers in \cite{MR1129143} which has similar goals to the Menger game when
played upon \(\oneptlind\kappa\).

\begin{game}
  Let \(\cloFillStrictGame\kappa\) denote the \term{strict union filling game}
  with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
  \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
  \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
  by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).

  \(\pl F\) wins the game if
  \(\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n\); otherwise, \(\pl C\)
  wins.
\end{game}

In \(\menGame{\oneptlind\kappa}\), \(\pl C\) essentially chooses a countable set
to not include in her neighborhood of \(\infty\), followed by \(\pl F\) choosing
a finite subset of this complement to cover during each round. Thus,
\(\pl F\) need only be concerned with the \textit{intersection} of the
countable sets chosen by \(\pl C\) in \(\menGame{\oneptlind\kappa}\), rather
than the union as in \(\cloFillStrictGame\kappa\).

Another difference: Scheepers required that \(\pl C\) always choose strictly
growing countable sets. The reasoning is clear: if the goal is to study tactics,
then \(\pl C\) cannot be allowed to trap \(\pl F\) in a loop by repeating the same
moves. But by eliminating this requirement, the study can then turn to Markov
strategies, bringing the game further in line with the Menger game played upon
\(\oneptlind\kappa\).

We introduce a few games to make the relationship between Scheeper's
\(\cloFillStrictGame\kappa\) and \(\menGame{\oneptlind\kappa}\) more precise.

\begin{game}
  Let \(\cloFillGame\kappa\) denote the
  \term{union filling game} which proceeds analogously
  to \(\cloFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
  is reduced to \(C_{n+1}\supseteq C_n\).
\end{game}

\begin{game}
  Let \(\cloFillInitialGame\kappa\) denote the
  \term{initial filling game} which proceeds analogously
  to \(\cloFillGame\kappa\), except that \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq C_0\).
\end{game}

\begin{game}
  Let \(\cloFillIntGame\kappa\) denote the
  \term{intersection filling game} which proceeds analogously
  to \(\cloFillInitialGame\kappa\), except that \(\pl C\) may choose any
  \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n\).
\end{game}

@@

\begin{theorem}
For any cardinal \(\kappa>\omega\) and integer \(k<\omega\),
Figure \ref{fillingGamesDiagram} holds.
\end{theorem}

\begin{proof}
  \(\pl F \kmarkwin{k}\menGame{\oneptlind\kappa}
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillIntGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\menGame{\oneptlind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
  countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
  into the open cover \([C]^1\cup\{\oneptlind\kappa\setminus C\}\)
  (resp. finite sequence of such open covers). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      C\cap\sigma(\mc U(s\concat\<C\>),n)
    \]
  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillIntGame\kappa\).

  \(\pl F \kmarkwin{k}\cloFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\menGame{\oneptlind\kappa}\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\cloFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
  cover \(\mc U\) of \(\oneptlind\kappa\) (resp. finite sequence \(s\) of such covers)
  into a countable set \(C\) which is the complement of some neighborhood of
  \(\infty\) in \(\mc U\) (resp. finite sequence of such countable sets).
  Then \(\tau\) defined by
    \[
      \tau(s\concat\<\mc U\>,n)
        =
      (\oneptlind\kappa\setminus C(\mc U))
        \cup
      \sigma(C(s\concat\<\mc U)\>),n)
    \]
  is a winning \(k\)-mark for \(\pl F\) in \(\menGame{\oneptlind\kappa}\).

  \(\pl F \kmarkwin{k}\cloFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\cloFillIntGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
  in \(\cloFillInitialGame\kappa\).

  \(\pl F \kmarkwin{k}\cloFillInitialGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillGame\kappa\): Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\cloFillInitialGame\kappa\). For each finite sequence \(s\), let \(t\preceq s\) mean \(t\)
  is a final subsequence of \(s\). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      \bigcup_{t\preceq s, m\leq n}
      \sigma(t\concat\<C\>,m)
    \]
  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillGame\kappa\).

  \(\pl F \kmarkwin{k}\cloFillGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\cloFillGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
  in \(\cloFillInitialGame\kappa\).

  \(\pl F \ktactwin{k}\cloFillStrictGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-tactic for \(\pl F\) in
  \(\cloFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
  be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
  Then \(\tau\) defined by
    \[
      \tau(\<C_0,\dots,C_i\>,n)
        =
      \sigma(\<C_0+(n-i),\dots,C_i+n\>)
    \]
  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillGame\kappa\).
\end{proof}

While we have not proven a direct implication between the Menger game and
Scheeper's original filling game, Scheepers introduced the statement
\(\alcompS\kappa\) relating to the almost-compatability of functions
from countable subsets of \(\kappa\) into \(\omega\) which may be applied to
both.

\begin{definition}
  For two functions \(f,g\) we say \(f\) is \textbf{\(\mu\)-almost compatible} with
  \(g\) (\(f\alcomp_\mu g\)) if \(|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu\).
  If \(\mu=\omega\) then we say \(f,g\) are \textbf{almost compatible}
  (\(f\alcomp g\)).
\end{definition}

\begin{definition}
  \(\alcompS\kappa\) states that there exist functions
  \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\omega}\) such that
  \(|\{\alpha\in A:f_A(\alpha)\leq n\}|<\omega\) for all \(n<\omega\) and
  \(f_A\alcomp f_B\) for all \(A,B\in[\kappa]^\omega\).
  \footnote{
  This is equivalent to the original characterization given in
  \cite{MR1129143}: there exist injections \(g_A:A\to\omega\)
  such that \(g_A\alcomp g_B\) for all \(A,B\in[\kappa]^\omega\) and \(A\subset B\).
  }
\end{definition}

Scheepers went on to show that \(\alcompS\kappa\) implies
\(\pl F \ktactwin2 \cloFillStrictGame\kappa\). This proof, along with the following
facts, give us inspiration for
finding a winning \(2\)-Markov strategy in the Menger game played on
\(\oneptlind\kappa\).

\begin{theorem}
  \(\alcompS{\omega_1}\) and \(\kappa>2^\omega\Rightarrow\neg\alcompS\kappa\)
  are theorems of \(ZFC\).
  \(\alcompS{2^\omega}\) is a theorem of \(ZFC+CH\) and consistent with
  \(ZFC+\neg CH\).
\end{theorem}

\begin{proof}
  For \(\alcompS{\omega_1}\), look at pg. 70 of \cite{MR597342}; this of course
  implies \(\alcompS{2^\omega}\) under \(CH\).
  \(\neg\alcompS{(2^\omega)^+}\) is shown by a cardinality argument
  in \cite{MR1129143}.
  The consistency result under \(ZFC+\neg CH\)
  is a lemma for the main theorem in \cite{MR1129143}.
\end{proof}

@@

%     &
%     &
%     \pl F \ktactwin2\cloFillStrictGame\kappa \\
%   };
%   \path[>=latex,->]
%     (m-2-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2)
%     (m-2-1) edge (m-3-3)
%     (m-1-2) edge (m-2-2)
%     (m-1-3) edge (m-2-3)
%     (m-3-3) edge (m-2-3);
%   \path[>=latex,<->]
%     (m-1-2) edge (m-1-3)
%     (m-2-2) edge (m-2-3);
% \end{tikzpicture}
\end{center}
\caption{Diagram of Filling/Menger game implications with \(\alcompS\kappa\)}
\label{fillingGamesDiagram2}
\end{figure}

\begin{theorem}
  \(\alcompS\kappa\) implies the game-theoretic results in
  Figure \ref{fillingGamesDiagram2}.
\end{theorem}
